On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 arity1.tex
Add files via upload

As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$. Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.
%\begin{enumerate}
\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}. Therefore, it needs to make three new bonds to deterministically stabilize $i$.\\

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (0.5, 0.866);
        \draw (0.5, 0.866) -- (-0.5, 0.866);
        \draw (0.0, 1.732) -- (-0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
      \end{tikzpicture}

      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
        \fill (0.0, 0.0) circle [radius = 0.1];
        \fill (-0.5, 0.866) circle [radius = 0.1];
        \fill (0.5, 0.866) circle [radius = 0.1];
        \fill (0.0, 1.732) circle [radius = 0.1];
        \fill (0.0, 0.0) node [below] {$(0, 0)$};
        \draw (0.0, 0.0) -- (-0.5, 0.866);
        \draw (-0.5, 0.866) -- (0.5, 0.866);
        \draw (0.0, 1.732) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
      \end{tikzpicture}

    \end{tabular}
    \caption{Two conformations when bead $i-1$ at (0,0) has a free hand}
    \label{fig:beadi}
  \end{center}
\end{figure}

@@

    \end{tabular}
    \caption{When beads $i, i+1, i+2$ make three hydrogen bonds \newline (c) there is an inactive bead at (-1,0). \newline (d) there is no bead at (-1,0).}
    \label{fig:3bonds}
  \end{center}
\end{figure}

@@

    \end{tabular}
    \caption{When beads $i+1, i+2, i+3$ make three hydrogen bonds \newline (a) there is an inactive bead at (1,0). \newline (b) there is no bead at (1,0).}
    \label{fig:3bonds2}
  \end{center}
\end{figure}

%\end{enumerate}

\end{proof}

>>>>

As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$. Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.\\
%\begin{enumerate}
\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities (see Fig.~\ref{fig:beadi2}, except it starts from (0,0) not (1,1)). Therefore, it needs to make three new bonds to deterministically stabilize $i$.\\

%\begin{figure}
%  \begin{center}
%    \begin{tabular}{cc}
%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
%        \fill (0.0, 0.0) circle [radius = 0.1];
%        \fill (0.5, 0.866) circle [radius = 0.1];
%        \fill (-0.5, 0.866) circle [radius = 0.1];
%        \fill (0.0, 1.732) circle [radius = 0.1];
%        \fill (0.0, 0.0) node [below] {$(0, 0)$};
%        \draw (0.0, 0.0) -- (0.5, 0.866);
%        \draw (0.5, 0.866) -- (-0.5, 0.866);
%        \draw (0.0, 1.732) -- (-0.5, 0.866);
%        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
%        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
%      \end{tikzpicture}
%
%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
%        \fill (0.0, 0.0) circle [radius = 0.1];
%        \fill (-0.5, 0.866) circle [radius = 0.1];
%        \fill (0.5, 0.866) circle [radius = 0.1];
%        \fill (0.0, 1.732) circle [radius = 0.1];
%        \fill (0.0, 0.0) node [below] {$(0, 0)$};
%        \draw (0.0, 0.0) -- (-0.5, 0.866);
%        \draw (-0.5, 0.866) -- (0.5, 0.866);
%        \draw (0.0, 1.732) -- (0.5, 0.866);
%        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
%        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
%      \end{tikzpicture}
%
%    \end{tabular}
%    \caption{Two conformations when bead $i-1$ at (0,0) has a free hand}
%    \label{fig:beadi}
%  \end{center}
%\end{figure}

@@

    \end{tabular}
    \caption{When beads $i, i+1, i+2$ make three hydrogen bonds (c) there is an inactive bead at (-1,0).  (d) there is no bead at (-1,0).}
    \label{fig:3bonds}
  \end{center}
\end{figure}

@@

    \end{tabular}
    \caption{When beads $i+1, i+2, i+3$ make three hydrogen bonds (a) there is an inactive bead at (1,0). (b) there is no bead at (1,0).}
    \label{fig:3bonds2}
  \end{center}
\end{figure}

\qed
\end{proof}
